\system: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-06 paper.tex
title change

\twocolumn[
\icmltitle{Inducing Domain Specific Languages for Bayesian Program Learning}

@@

What DSL does \system learn?
The learned DSL contains templates for polynomials of different orders,
which lets the algorithm quickly hone in on the kinds of functions that are most appropriate to this domain (Table~\ref{regressionDSL}).
Examining the programs themselves,
one finds that the algorithm discovers representations for each of the polynomials that minimizes the number of continuous degrees of freedom:
for example, it represents the linear function $-x+2$ with the program 
\texttt{(* (* (+ x }$\mathcal{R}$\texttt{) }$\mathcal{R}$\texttt{) x)}, which has two continuous degrees of freedom -- while representing quartic functions using the invented DSL primitive $f_6$ in Table~\ref{regressionDSL}.
This falls out of our Bayesian treatment of the program learning problem -- both the bias towards shorter programs (more likely under $\mathcal{D},\theta$) and the likelihood's model BIC penalty.
\begin{table}
\begin{tabular}{l}
  \toprule
  %% Primitives& $+,\times:\mathbb{R}\to \mathbb{R}\to \mathbb{R}$\\
  %% & $\mathcal{R}:\mathbb{R}$ (real valued parameter)\\\midrule
  %% Observation $x$& $N$ input/output examples: $\left\{(i_n,o_n) \right\}_{n\leq N}$\\
  %% \midrule
  %% Likelihood $\probability[x|p]$& $\propto\exp\left( - D\log N \right)\prod_{n\leq N}\mathcal{N}(p(i_n)|o_n)$
  %% \\\midrule
    $f_0 = $\texttt{(+ }$\mathcal{R}$\texttt{)}\\
    $f_1($\texttt{x}$) =$ \texttt{(* (* (+ x }$\mathcal{R}$\texttt{) }$\mathcal{R}$\texttt{) x)} \\
      $f_2($\texttt{x}$) =$ \texttt{(+ }$\mathcal{R}$\texttt{ ($f_1$ x))} \\
      $f_3($\texttt{x}$) = $\texttt{(* x (}$f_2$\texttt{ x))}\\
  $f_4($\texttt{x}$) = $\texttt{(}$f_0$\texttt{ (}$f_3$\texttt{ x)))}\\
  $f_5($\texttt{x}$) =$ \texttt{(* x (}$f_4$\texttt{ x))}\\
  $f_6($\texttt{x}$) = $\texttt{(}$f_0$\texttt{ (}$f_4$\texttt{ x))} (\emph{4th order polynomial})
  \\\bottomrule
\end{tabular}
\caption{Some induced DSL primitives for symbolic regression. System starts out with addition, multiplication, and real numbers, and learns functions for building 4th order polynomials.}\label{regressionDSL}
\end{table}

>>>>

\twocolumn[
\icmltitle{\system: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning}

@@

What DSL does \system learn?
The learned DSL contains templates for polynomials of different orders,
which lets the algorithm quickly hone in on the kinds of functions that are most appropriate to this domain (Table~\ref{regressionDSL}).
Examining the programs themselves,
one finds that the algorithm discovers representations for each of the polynomials that minimizes the number of continuous degrees of freedom:
for example, it represents the linear function $-x+2$ with the program 
\texttt{(* (* (+ x }$\mathcal{R}$\texttt{) }$\mathcal{R}$\texttt{) x)}, which has two continuous degrees of freedom -- while representing quartic functions using the invented DSL primitive $f_6$ in Table~\ref{regressionDSL}.
This falls out of our Bayesian treatment of the program learning problem -- both the bias towards shorter programs (more likely under $\mathcal{D},\theta$) and the likelihood model's BIC penalty.
\begin{table}
\begin{tabular}{l}
  \toprule
  %% Primitives& $+,\times:\mathbb{R}\to \mathbb{R}\to \mathbb{R}$\\
  %% & $\mathcal{R}:\mathbb{R}$ (real valued parameter)\\\midrule
  %% Observation $x$& $N$ input/output examples: $\left\{(i_n,o_n) \right\}_{n\leq N}$\\
  %% \midrule
  %% Likelihood $\probability[x|p]$& $\propto\exp\left( - D\log N \right)\prod_{n\leq N}\mathcal{N}(p(i_n)|o_n)$
  %% \\\midrule
    $f_0 = $\texttt{(+ }$\mathcal{R}$\texttt{)}\\
    $f_1($\texttt{x}$) =$ \texttt{(* (* (+ x }$\mathcal{R}$\texttt{) }$\mathcal{R}$\texttt{) x)} \\
      $f_2($\texttt{x}$) =$ \texttt{(+ }$\mathcal{R}$\texttt{ ($f_1$ x))} \\
      $f_3($\texttt{x}$) = $\texttt{(* x (}$f_2$\texttt{ x))}\\
  $f_4($\texttt{x}$) = $\texttt{(}$f_0$\texttt{ (}$f_3$\texttt{ x)))}\\
  $f_5($\texttt{x}$) =$ \texttt{(* x (}$f_4$\texttt{ x))}\\
  $f_6($\texttt{x}$) = $\texttt{(}$f_0$\texttt{ (}$f_4$\texttt{ x))} (\emph{4th order polynomial})
  \\\bottomrule
\end{tabular}
\caption{Some induced DSL primitives for symbolic regression. System starts out with addition, multiplication, and real numbers, and learns functions for building 4th order polynomials.}\label{regressionDSL}
\end{table}
